Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-21 journal/article.tex
Having a positive experience

>>>>

% Having a positive experience

It is clear that any positive results will facilitate an organizational
transformation. Although a recipie to fabricate positive experiences can not be
given, many cases described how they had succeeded. Benefield [P6] describes how
a survey was done to objectively measure satisfaction in agile, and the positive
results helped teams make the decision to change their way of working. Another
case describes how the corporate agile awareness and teaching event was designed
to be fun and engaging, which made people take more ethusiasm in applying the
agile practices [P32]. The move towards agile is assisted by making any benefits
publicly visible and celebrating even the small victories [P40, P42].

The dynamics of positive results were explained in further ways. Several cases
highlighted that the agile transformation was spread effectively through
positive word-of-mouth [P6, P40]. When good results were shown by a team it
created interest in others, and enthusiasm to try the new model will spread
[P39, P46]. Some companies were using agile and waterfall methods side by side.
This setting made it comparison possible, bringing up the benefits of the agile
model [P19, P36].
